\begin{abstract}

Measuring the correlation (or similarity) between different time series is a basic prerequisite for mining time series data. Traditional measures, such as Dynamic Time Warping (DTW), relies on the notion that two time series are similar if their have a lot of similar sub-patterns. However, there are many real-world scenarios where time series, having different overall patterns (e.g. Periodical, Linear, random, etc.), are still of common interest because they all change their behavior simultaneously. However, despite the importance of heterogenous time data, there has been little prior work addressing the correlation between two types of heterogeneous time series data.

In this paper, we propose a change based correlation measure, for mining heterogeneous time series. Our measure is ideally suited for heterogenous time series data commonly found in medical and high performance computing (HPC) domain. Furthermore, our measure admits locality sensitive hashing (LSH) scheme, leading to efficient sub-linear search and clustering algorithms. Existing of LHS makes our proposed measure ideal and practical for massive datasets. Rigorous experimental evaluations over seven real and synthetic datasets clearly demonstrates the significant effectiveness and efficiency of our proposal over popular measures.
\end{abstract}
% A category with the (minimum) three required fields
\category{H.2.8}{Database Management}{Data Mining}

\terms{Application}

\keywords{Correlation, Time Series, Hashing Learning} 